Creating enriched heatmaps

### 2020-08-23 Scripts_for_results/06_creating_enriched_heatmaps.Rmd
updated results scripts

>>>>

########################################3

# Plotting

```{r}

pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))

e=5
norm_mat_pt_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_ctcf <- colSums(norm_mat_pt_ctcf[])
norm_mat_pt_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_rad21 <- colSums(norm_mat_pt_rad21[])
norm_mat_pt_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_smc3 <- colSums(norm_mat_pt_smc3[])
norm_mat_pt_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_znf143 <- colSums(norm_mat_pt_znf143[])

norm_mat_a_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_a_ctcf <- colSums(norm_mat_a_ctcf[])
norm_mat_a_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_a_rad21 <- colSums(norm_mat_a_rad21[])
norm_mat_a_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_a_smc3 <- colSums(norm_mat_a_smc3[])
norm_mat_a_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_a_znf143 <- colSums(norm_mat_a_znf143[])

df <- data.frame(X = rep(c(1:200),8),
                 E = c(norm_mat_pt_ctcf,
                       norm_mat_pt_rad21,
                       norm_mat_pt_smc3,
                       norm_mat_pt_znf143,
                       norm_mat_a_ctcf,
                       norm_mat_a_rad21,
                       norm_mat_a_smc3,
                       norm_mat_a_znf143),
                 Tool = c(rep("preciseTAD", 200*4),
                          rep("Arrowhead", 200*4)),
                 A = rep(c(rep("CTCF", 200),
                       rep("RAD21", 200),
                       rep("SMC3", 200),
                       rep("ZNF143", 200)),2))

ggplot(data=df, aes(x=X, y=E/5000, group=Tool, color=Tool)) +
  facet_grid(. ~ A) +
  geom_line(alpha=.75, size=1.5) +
  xlab("Distance from boundary (kb)") +
  ylab("") +
  scale_color_manual(name="Tool", 
                       values=c("blue", "forestgreen"))+
  scale_x_continuous(breaks=c(0,100,200),
                     label=c("-5", "Center", "5")) +
  theme_minimal() +
    theme_bw()+
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 20),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text.x = element_text(size = 20),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=20),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = "bottom")

################################################################################

pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

e=10
norm_mat_pt_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_ctcf <- colSums(norm_mat_pt_ctcf[])
norm_mat_pt_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_rad21 <- colSums(norm_mat_pt_rad21[])
norm_mat_pt_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_smc3 <- colSums(norm_mat_pt_smc3[])
norm_mat_pt_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_znf143 <- colSums(norm_mat_pt_znf143[])

norm_mat_p_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_p_ctcf <- colSums(norm_mat_p_ctcf[])
norm_mat_p_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_p_rad21 <- colSums(norm_mat_p_rad21[])
norm_mat_p_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_p_smc3 <- colSums(norm_mat_p_smc3[])
norm_mat_p_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_p_znf143 <- colSums(norm_mat_p_znf143[])

df <- data.frame(X = rep(c(1:400),8),
                 E = c(norm_mat_pt_ctcf,
                       norm_mat_pt_rad21,
                       norm_mat_pt_smc3,
                       norm_mat_pt_znf143,
                       norm_mat_p_ctcf,
                       norm_mat_p_rad21,
                       norm_mat_p_smc3,
                       norm_mat_p_znf143),
                 Tool = c(rep("preciseTAD", 400*4),
                          rep("Peakachu", 400*4)),
                 A = rep(c(rep("CTCF", 400),
                       rep("RAD21", 400),
                       rep("SMC3", 400),
                       rep("ZNF143", 400)),2))

ggplot(data=df, aes(x=X, y=E/10000, group=Tool, color=Tool)) +
    facet_grid(. ~ A) +
    geom_line(alpha=.75, size=1.5) +
    xlab("Distance from boundary (kb)") +
    ylab("") +
    scale_color_manual(name="Tool", 
                       values=c("red", "forestgreen"))+
    scale_x_continuous(breaks=c(0,200,400),
                       label=c("-10", "Center", "10")) +
    theme_minimal() +
    theme_bw()+
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 20),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text.x = element_text(size = 20),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=20),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = "bottom")
```
